### 2022-04-01 manuscript/thesis.tex
revisions to sections 3 and 4

\usepackage{framed}
\usepackage{changepage}
\usepackage{amsfonts}
\usepackage{listings}
\usepackage[svgnames]{xcolor}
\usepackage{graphicx}
\usepackage{subfig}
% Standard, old-style thesis
\usepackage{isutraditional}   
\chaptertitle
% Old-style, thesis numbering down to subsubsection
\alternate
% \nochap
\usepackage{rotating}
% Bibliography without numbers or labels
\usepackage{natbib}
% Use the following line if you want square brackets and numbering system
% \usepackage[square, numbers]{natbib}
% \lstset{language=R,
%     basicstyle=\small\ttfamily,
%     stringstyle=\color{DarkGreen},
%     otherkeywords={0,1,2,3,4,5,6,7,8,9},
%     morekeywords={TRUE,FALSE},
%     deletekeywords={data,frame,length,as,character},
%     keywordstyle=\color{blue},
%     commentstyle=\color{DarkGreen},
% }
\makeatletter

@@

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[intoc, english]{nomencl}
\renewcommand{\chaptername}{}
\usepackage{Sweave}
\begin{document}
\input{thesis-concordance}
\DeclareGraphicsExtensions{.jpg,.pdf,.mps,.png}
%\begin{singlespace}
\def\@makechapterheada{\vspace*{-2cm}\titlepage} % in order to reduce the space between margin and heading in titlepage
\include{Preface/titlepage}
%\end{singlespace}

@@

\begin{table}[h!]
\centering
 \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
 \hline
    location & target & type & unit & family & param1 & param2 & weight
    \\ \hline
    US National & Season Onset & Dist & week & norm & $a_n$ & $b_n$ & $w_1$\\
    US National & Season Onset & Dist & week & lnorm & $a_l$ & $b_l$ & $w_2$\\
    ... & ... & ... & ... & ... & ... & ... & ...\\
 \hline
 \end{tabular}
 \begin{minipage}{11cm}
\captionsetup{font=scriptsize}
 \caption[Mixture distribution forecast submission example]{This is an example 
 of a 
 submission file
 for a disease outbreak forecast using a mixture distribution representation.
 Each row represents a component of a mixture distribution. The variables
 location, target, and unit specify what is being forecasted. The variable type
 specifies that the row represents a parametric distribution. The variables
 family, param1, and param2 specify the exact distribution. And the variable 
 weight specifies the weight $w_i$ that the component distribution has in the
 mixture distribution. Here two components are shown with distributions
 Normal$(a_n, b_n)$, Lognormal$(a_l, b_l)$ and weights $w_1$ and $w_2$.}
 \label{table:mstan}
 \end{minipage}
\end{table}

@@

\begin{table}[h!]
\centering
 \begin{tabular}{|c|c|c|c|c|}
 \hline
    family & param1 & param2 & param3 & weight
    \\ \hline
    Lnorm & 2 & 1 & NA & 0.3  \\
    Norm & 2.1 & 1 & NA & 0.7 \\
 \hline
 \end{tabular}
 \caption[Illustrative forecast 1]{Toy prediction 1}
 \label{tab:preddf1}
\end{table}

\begin{table}[h!]
\centering
 \begin{tabular}{|c|c|c|c|c|}
 \hline
    family & param1 & param2 & param3 & weight
    \\ \hline
    Norm & 1.5 & 1 & NA & 0.4  \\
    Norm & 4 & 2 & NA & 0.6 \\
 \hline
 \end{tabular}
 \caption[Illustrative forecast 2]{Toy prediction 2}
 \label{tab:preddf2}
\end{table}

Here we include code to illustrate the process of constructing and scoring two 
separate forecasts. We suppose that Table \ref{tab:preddf1} represents a 
submitted forecast from one forecaster and Table \ref{tab:preddf2} represents
a forecast of the same event from a second forecaster.
Note the additional \texttt{param3} variable
in Tables \ref{tab:preddf1} and \ref{tab:preddf1}. This variable is included
in the table because of the functionality of the \texttt{MakeDist()} function
which allows for component distributions of three parameters.
The code here shows these two forecasts as \texttt{data.frame}s and how the 
\texttt{MakeDist()} 
function is used to create the distributions in \texttt{R}. Once the 
distributions are created as \texttt{AbscontDistribution} objects, then 
functions for evaluating a pdf and a CDF for each are created.

\begin{Schunk}
\begin{Sinput}
> preddf1
> #  family param1 param2 param3 weights
> #1  Lnorm    2.0      1     NA     0.3
> #2   Norm    2.1      1     NA     0.7
> 
> preddf2
> #  family param1 param2 param3 weights
> #1   Norm    1.5      1     NA     0.4
> #2   Norm    4.0      2     NA     0.6
> 
> 
> 
> #make mixture distributions from prediction submissions
> mdist1 <- MakeDist(preddf1)
> mdist2 <- MakeDist(preddf2)
> #make pdfs for mixture predictions
> dmdist1 <- function(x) {distr::d(mdist1)(x)}
> dmdist2 <- function(x) {distr::d(mdist2)(x)}
> #make cdfs for mixture predictions
> pmdist1 <- function(x) {distr::p(mdist1)(x)}
> pmdist2 <- function(x) {distr::p(mdist2)(x)}
\end{Sinput}
\end{Schunk}

\begin{figure}[htbp]
\centerline{\includegraphics[scale=.15]{Images/toyfors12.png}}
\caption[Toy mixture distributions]{These plots show the density functions of
the two toy mixture distribution forecasts along with the component density
functions scaled by the corresponding weights}
\label{fig:toymixs}
\end{figure}

The LogS or the CRPS may then be calculated for each forecast using the pdf
and cdf functions respectively. Here will will assume that the realized value
which both forecasts attempted to predict was 3. The \texttt{CRPS()} function 
here is 
included in the appendix of this manuscript. It can be seen here that by the 
LogS, the forecast from table \ref{tab:preddf1} outperforms that from table
\ref{tab:preddf2}. Yet under the CRPS the performance is the other way around.

\begin{Schunk}
\begin{Sinput}
> #realized observation
> ob <- 3
> #LogS for predictions at the realized observation
> -log(dmdist1(ob)) # => 1.547238
> -log(dmdist2(ob)) # => 1.848796
> #CRPS for predictions at the realized observation
> CRPS(pmdist1,y=ob) # => 0.6348212
> CRPS(pmdist2,y=ob) # => 0.5306083
\end{Sinput}
\end{Schunk}

\section{Ensemble construction}

To construct an ensemble distribution from multiple mixture distributions, the 
\texttt{UnivarMixingDistribution} is again a useful tool. The function takes 
two or more
\texttt{AbscontDistribution} or mixture distributions and a vector of weights 
corresponding to each mixture. A new \texttt{AbscontDistribution} object is 
returned as an ensemble of mixture distributions see (\ref{eq:bma}).

At the onset of a collaborative forecast before the various models can be scored
based on true observations, it may make sense to assign equal weight to each 
component distribution in an ensemble. As a project progresses however, 
assigning weights based on past performance may be desired. As mentioned in 
section \ref{section:pardist}, weights may be selected by maximizing the
likelihood of (\ref{eq:bma}) or by minimizing the CRPS. Another method of 
selecting weights is to use the posterior model probability.

If we have $T$ models ($M_t$) the posterior model probability of $M_t$ is 
defined as

\begin{equation}
\label{eq:pmp}
p(M_t|x) = \frac{p(x|M_t)p(M_t)}{p(x)}
         = \frac{p(x|M_t)p(M_t)}{\sum_{k=1}^T p(x|M_k)p(M_k)}
\end{equation}
where $p(\cdot |M_t) := p_m(\cdot)$ is the density function of the model and 
$p(M_j)$ is the prior probability assigned to the model. Where the prior
probabilities for each model are equal or $p(M_t) = 1/T$ for all $t$ 
(\ref{eq:pmp}) is reduced to

@@

The posterior model probability $p(M_t|x^*)$ for an already observed event $x^*$
are then used as weights for a yet unrealized event being forecasted i.e.
$w_t := p(M_t|x^*)$ see (\ref{eq:bma}).

From the same toy problem in the previous section, the following code shows how
to use the posterior model probability to select weights and construct an 
ensemble distribution and score the ensemble forecast. The ensemble distribution
with components is show in figure \ref{fig:mixense}.

\begin{Schunk}
\begin{Sinput}
> #posterior model probability for calculating weights
> w1 <- pmdist1(ob)/(pmdist1(ob) + pmdist2(ob))
> w2 <- 1-w1
> #w1 => 0.5286434
> #w2 => 0.4713566
> 
> #build ensemble with calculated weights
> ensdist <- distr::UnivarMixingDistribution(mdist1,
+                                            mdist2,
+                                            mixCoeff = c(w1,w2))
> #pdf and cdf for ensemble
> densdist <- function(x) {(distr::d(ensdist)(x))}
> pensdist <- function(x) {(distr::p(ensdist)(x))}
> #LogS for predictions at the realized observation
> -log(densdist(ob)) # => 1.678156
> #CRPS for predictions at the realized observation
> CRPS(pensdist,y=ob) # => 0.5486368
\end{Sinput}
\end{Schunk}

\begin{figure}[htbp]
\centerline{\includegraphics[scale=.15]{Images/mix_ense.png}}
\caption[Toy ensemble forecast]{Toy ensemble forecast with component mixture
distributions shown}
\label{fig:mixense}
\end{figure}

@@

\chapter{Retrospective Analysis}
\label{section:retrostud}

For large collaborative forecast projects having already established the 
representation formats for forecasting, it may be difficult for individual
forecast teams to adjust to a discrete mixture distribution format. Exact 
methods for modeling and forecasting may not cater well to submitting a forecast
as a discrete parametric mixture distribution.

In this section we attempt to assess whether or not any forecasts from the CDC
influenza forecast competition and the COVID-19 Forecast Hub were generated from
common continuous parametric distributions. The forecasts we assess are in the 
forms of discretized bin predictions or sets of predictive intervals. In these
formats, not knowing anything about distributions or samples,  formal 
statistical methods for fitting to parametric distributions 
and assessing fit do not exist. Thus any results stated here may not be stated
in terms of statistical certainty.

\section{CDC Influenza like Illness}
The CDC Retrospective Forecasts project at zoltrdata.com (cite??) contains over
850,000 probabilistic influenza-like illness predictions for all combinations
of eleven regions 
in the United States and seven targets from twenty-seven different models. These
include predictions during Influenza season between October 2010 and December
2018. All predictions are in the form of discretized probability bins.

We wanted to determine whether or not some or any of these binned forecasts were
generated from known uniform, normal, 
lognormal or gamma continuous distribution families. 
The process we followed for making such a claim was
to fit a distribution to the probabilities provided in the forecast by
minimizing

\begin{equation}
  \sum_{i=1}^K (p_i - [F(b_i; \theta) - F(b_{i-1}; \theta)])^2
  \label{eq:mds}
\end{equation}

Here $F(\cdot; \hat{\theta})$ is a CDF, $p_i$ is the reported probability for 
the $i^{th}$ bin $B_i := [b_{i-1}, b_i)$ and $K$ is the number of bins.
The fitted parameter vector $\hat{\theta}$ is the solution to

\begin{equation}
\arg\min_{\theta}\sum_{i=1}^K (p_i - 
[F(b_i; \theta) - F(b_{i-1}; \theta)])^2
\label{eq:discfit}
\end{equation}

If a well known continuous distribution was fit to the submitted binned 
prediction
and the mean sum of squared differences (MSD) or \ref{eq:msd} fell below a 
specified cutoff value, we
considered that the binned predictions were plausibly discretized from the 
continuous distribution.

To determine what values to use as cutoffs we conducted a study where 
binned distributions were discretized from known continuous distributions, 
parameters were fit to the binned distrubtions and the MSD was calculated.

For each of uniform, truncated normal (TN), truncated lognormal (TL) and 
truncated gamma (TG) distributions the following was
done 1,000 times. A set of 131 bins with interval lengths of 
0.1 between 0 and 13.1 was constructed. 
A value $\mu$ was selected from a $Uniform(a,b)$ distribution and $\sigma$ from 
a $Uniform(.05,1.6)$ distribution. $\mu$ and $\sigma$ were taken as respectively 
the center and scale parameters of a TN distribution. 
For uniform, TL and TG family
distributions, model parameters were solved for so that $\mu$ and $\sigma$ 
were roughly the mean and standard deviation. The minimization was done using 
the \texttt{optim} function in the \texttt{R} \texttt{stats} package.
Had we accounted for the changes
in moment values from the truncation, the means and standard deviations could 
have been exactly $\mu$ and $\sigma$. But we considered the differences small 
enough that it didn't matter for our purpose.

With a known distribution, probabilities $p_i =F(b_i; \theta) - F(b_{i-1})$ were
calculated for each bin. A uniform or truncated distribution from the same
family was fit to the bins by minimizing \ref{eq:msd} with the resulting
distribution function $F(\cdot; \hat{\theta})$. From the fitted distribution
$\hat{p_i} = F(b_i; \hat{\theta}) - F(b_{i-1}; \hat{\theta})$ was computed for 
each of the 131 bins. Finally the mean sum of squared probability differences
$\frac{1}{K}\sum_{i=1}^K (\hat{p_i} - p_i)^2$ was calculated. 
Table \ref{table:bincutoffs}
below shows MSD value for which 95\% of all 1,000 MSDs fell below. Those values 
were selected as the 
cutoff values for declaring whether or not a binned distribution was discretized
from a common continuous distribution.

\begin{table}[h!]
  \centering
  \begin{tabular}{l*{6}{c}r}
  Distribution          & MSD 95\%  \\
  \hline
  Uniform               & 8.809460e-05   \\
  Truncated Normal      & 1.126683e-07  \\
  Truncated Lognormal   & 3.877829e-06  \\
  Truncated Gamma       & 1.500152e-06  \\
  \end{tabular}
  \caption[Discretized bin distribution cutoff values]{If a binned 
  distribution is fit to a parametric distribution and the MSD is smaller than
  the corresponding cutoff value listed here, we consider that binned 
  distribution to have been discretized from the fit parametric distribution.}
  \label{table:bincutoffs}
\end{table}

Of the 869,638 predictions from the CDC Retrospective Forecast project, we fit
each of Uniform, TN, TL and TG distributions to 11,715 of the individual 
predictions. The MSD between the prediction probabilities and the fit
discretized probabilities was calcuated. For each prediction, the fitted 
distribution with the lowest MSD was considered the best fit and if the MSD fell
below the corresponding cutoff value listed in \ref{table:bincutoffs} we 
considered that 
the prediction was discretized from the fit distribution.

Of the 11,715 binned distributions fit to continuous parametric distributions,
2,502 of those fits producted MSD values below the values listed in table
\ref{table:bincutoffs}. Thus we conclude that a proportion of 0.214 of those
forecasts were generated from a common parametric distribution. The results for 
the
11,715 fit distributions, which families the binned distributions were best
fit to and whether or not the fits produce an MSD below the cutoff value, 
are seen in table \ref{table:cdcresults}. Figure \ref{fig:binparamfits} is an
example of
the best fit distributions to the same binned probability distribution.

\begin{table}[h!]
  \centering
  \begin{tabular}{l*{6}{c}r}
  Distribution Family   & Total    & Total below MSD cutoff value 
  & Proportion from parametric distribution\\
  \hline
  Uniform               & 896      & 669  & 0.747  \\
  Truncated Normal      & 3,804    & 198  & 0.052  \\
  Truncated Lognormal   & 4,501    & 1,340 & 0.289 \\
  Truncated Gamma       & 2,514    & 295   & 0.117 \\
  \end{tabular}
  \caption[CDC influenza retro analysis results]{Results for CDC influenza
  forecast retro analysis}
  \label{table:cdcresults}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics[scale=.15]{Images/flu_fit_17_10_3.png}}
\caption[Parametric distribution fits to binned distribution]{This figure shows
the plots of fits from each a uniform, truncated normal, truncated lognormal
and truncated gamma distributions to the same binned probability distribution.
In this case, the fit to the normal distribution produced an MSD below the 
normal cutoff value, so we conclude that the binned distribution may have been
discretized froma truncated normal.}
\label{fig:binparamfits}
\end{figure}

>>>>

\usepackage{framed}
\usepackage{changepage}
\usepackage{amsfonts}
\usepackage{listings}
\usepackage[svgnames]{xcolor}

\usepackage{graphicx}
\usepackage{subfig}
% Standard, old-style thesis
\usepackage{isutraditional}   
\chaptertitle
% Old-style, thesis numbering down to subsubsection
\alternate
% \nochap
\usepackage{rotating}
% Bibliography without numbers or labels
\usepackage{natbib}
% Use the following line if you want square brackets and numbering system
% \usepackage[square, numbers]{natbib}
% \lstset{language=R,
%     basicstyle=\small\ttfamily,
%     stringstyle=\color{DarkGreen},
%     otherkeywords={0,1,2,3,4,5,6,7,8,9},
%     morekeywords={TRUE,FALSE},
%     deletekeywords={data,frame,length,as,character},
%     keywordstyle=\color{blue},
%     commentstyle=\color{DarkGreen},
% }
\makeatletter

@@

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[intoc, english]{nomencl}
\renewcommand{\chaptername}{}

\usepackage{Sweave}
\begin{document}
\input{thesis-concordance}
\DefineVerbatimEnvironment{Sinput}{Verbatim} {xleftmargin=2em,
                                              frame=single}
\DefineVerbatimEnvironment{Soutput}{Verbatim}{xleftmargin=2em,
                                              frame=single}
\DeclareGraphicsExtensions{.jpg,.pdf,.mps,.png}

%\begin{singlespace}
\def\@makechapterheada{\vspace*{-2cm}\titlepage} % in order to reduce the space between margin and heading in titlepage
\include{Preface/titlepage}
%\end{singlespace}

@@

\begin{table}[h!]
\centering
 \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
 \hline
    location & target & type & unit & family & param1 & param2 & weight
    \\ \hline
    us national & season onset & dist & week & norm & $a_n$ & $b_n$ & $w_1$\\
    us national & season onset & dist & week & lnorm & $a_l$ & $b_l$ & $w_2$\\
    ... & ... & ... & ... & ... & ... & ... & ...\\
 \hline
 \end{tabular}
 \begin{minipage}{11cm}
\captionsetup{font=scriptsize}
 \caption[Mixture distribution forecast submission example]{This is an example 
 of a 
 submission file
 for a disease outbreak forecast using a mixture distribution representation.
 Each row represents a component of a mixture distribution. The variables
 location, target, and unit specify what is being forecasted. The variable type
 specifies that the row represents a parametric distribution. The variables
 family, param1, and param2 specify the exact distribution. And the variable 
 weight specifies the weight $w_i$ that the component distribution has in the
 mixture distribution. Here two components are shown with distributions
 Normal$(a_n, b_n)$, Lognormal$(a_l, b_l)$ and weights $w_1$ and $w_2$.}
 \label{table:mstan}
 \end{minipage}
\end{table}

@@

\begin{table}[h!]
\centering
 \begin{tabular}{|c|c|c|c|c|}
 \hline
    family & param1 & param2 & param3 & weight
    \\ \hline
    Lnorm & 2 & 1 & NA & 0.3  \\
    Norm & 2.1 & 1 & NA & 0.7 \\
 \hline
 \end{tabular}
  \begin{minipage}{11cm}
\captionsetup{font=scriptsize}
 \caption[Illustrative forecast 1]{This is an illustrative example of a
 mixture distribution
 forecast where the distribution is described in a data frame. The first 
 component is a Lognormal$(2,1)$ with a weight of 0.3 in the mixture and the 
 second component is a Normal$(2.1,1)$ with a weight of 0.7.}
 \label{tab:preddf1}
 \end{minipage}
\end{table}

\begin{table}[h!]
\centering
 \begin{tabular}{|c|c|c|c|c|}
 \hline
    family & param1 & param2 & param3 & weight
    \\ \hline
    Norm & 1.5 & 1 & NA & 0.4  \\
    Norm & 4 & 2 & NA & 0.6 \\
 \hline
 \end{tabular}
  \begin{minipage}{11cm}
\captionsetup{font=scriptsize}
 \caption[Illustrative forecast 2]{This is a second
 illustrative example of a mixture distribution
 forecast where the distribution is described in a data frame. The first 
 component is a Normal$(1.5,1)$ with a weight of 0.4 in the mixture and the 
 second component is a Normal$(4,2)$ with a weight of 0.6.}
 \label{tab:preddf2}
 \end{minipage}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics[scale=.15]{Images/toyfors12.png}}
\begin{center}
 \begin{minipage}{11cm}
\captionsetup{font=scriptsize}
\caption[Example mixture distributions]{These plots show the density functions 
of
the two example mixture distribution forecasts along with the component density
functions scaled by the corresponding weights}
\label{fig:toymixs}
\end{minipage}
\end{center}
\end{figure}

Here we include code to illustrate the process of constructing and scoring two 
separate forecasts. We suppose that Table \ref{tab:preddf1} represents a 
submitted forecast from one forecaster and Table \ref{tab:preddf2} represents
a forecast of the same event from a second forecaster. Table \ref{fig:toymixs}
shows plots of the pdfs for both mixture forecasts.
Note the additional \texttt{param3} variable
in Tables \ref{tab:preddf1} and \ref{tab:preddf1}. This variable is included
in the table because of the functionality of the \texttt{MakeDist()} function
which allows for component distributions of up to three parameters.
The code here shows these two forecasts as \texttt{data.frame}s and how the 
\texttt{MakeDist()} 
function is used to create the distributions in \texttt{R}. Once the 
distributions are created as \texttt{AbscontDistribution} objects, then 
functions for evaluating a pdf and a CDF for each are created.

\begin{Schunk}
\begin{Sinput}
> preddf1
\end{Sinput}
\begin{Soutput}
  family param1 param2 param3 weights
1  Lnorm    2.0      1     NA     0.3
2   Norm    2.1      1     NA     0.7
\end{Soutput}
\begin{Sinput}
> preddf2
\end{Sinput}
\begin{Soutput}
  family param1 param2 param3 weights
1   Norm    1.5      1     NA     0.4
2   Norm    4.0      2     NA     0.6
\end{Soutput}
\begin{Sinput}
> #make mixture distributions from prediction submissions
> mdist1 <- MakeDist(preddf1)
> mdist2 <- MakeDist(preddf2)
\end{Sinput}
\end{Schunk}

\begin{Schunk}
\begin{Sinput}
> #make pdfs for mixture predictions
> dmdist1 <- function(x) {distr::d(mdist1)(x)}
> dmdist2 <- function(x) {distr::d(mdist2)(x)}
> #make cdfs for mixture predictions
> pmdist1 <- function(x) {distr::p(mdist1)(x)}
> pmdist2 <- function(x) {distr::p(mdist2)(x)}
\end{Sinput}
\end{Schunk}

The LogS or the CRPS may then be calculated for each forecast using the pdf
and CDF functions respectively. Here will will assume that the realized value
which both forecasts attempted to predict was \texttt{3}. 
The \texttt{CRPS()} function
here is one that we wrote and is
included in the APPENDIX. It is seen in the code below that under the
LogS, forecast 1 from table \ref{tab:preddf1} outperforms forecast 2 from table
\ref{tab:preddf2} with scores of 1.547 and 
1.849 respectively. 
However, under the CRPS forecast 2 outperforms forecast 1
with scores 0.635 and 
0.635 respectively. We continue to use these same
forecasts in Section \ref{section:enscon} to construct an ensemble forecast.

\begin{Schunk}
\begin{Sinput}
> #realized observation
> ob <- 3
> #LogS for predictions at the realized observation
> -log(dmdist1(ob))
\end{Sinput}
\begin{Soutput}
[1] 1.547238
\end{Soutput}
\begin{Sinput}
> -log(dmdist2(ob))
\end{Sinput}
\begin{Soutput}
[1] 1.848796
\end{Soutput}
\end{Schunk}

\begin{Schunk}
\begin{Sinput}
> #CRPS for predictions at the realized observation
> CRPS(pmdist1,y=ob)
\end{Sinput}
\begin{Soutput}
[1] 0.6348212
\end{Soutput}
\begin{Sinput}
> CRPS(pmdist2,y=ob)
\end{Sinput}
\begin{Soutput}
[1] 0.5306083
\end{Soutput}
\end{Schunk}

\section{Ensemble construction}
\label{section:enscon}

To construct an ensemble distribution from multiple mixture distributions, the 
\texttt{UnivarMixingDistribution()} is again a useful tool. The function takes 
two or more
\texttt{AbscontDistribution} distribution objects and a vector of weights 
corresponding to each object. A new \texttt{AbscontDistribution} object is 
returned as an ensemble of mixture distributions as in (\ref{eq:bma}). 
Since they are \texttt{AbscontDistribution} objects \texttt{mdist1} and 
\texttt{mdist2} created in the code
in Section \ref{section:tools} may be input as arguments into the function
\texttt{UnivarMixingDistribution()}, but weights for each object need to also
be determined.

At the onset of a collaborative forecast before there are true event 
observations which the forecasts can be scored on, 
it may make sense to assign an equal weight to each 
component distribution in an ensemble. As a project progresses however, 
assigning weights based on past performance may be desired. As mentioned in 
section \ref{section:pardist}, weights may be selected by maximizing the
likelihood of (\ref{eq:bma}) or by minimizing the CRPS. Another method of 
selecting weights is to use the posterior model probability.

If we have $T$ models ($M_t$) the posterior model probability of $M_t$ is 
defined as in \eqref{eq:pmp} where $p(\cdot |M_t) := p_m(\cdot)$ is the density 
function of the model and 
$p(M_j)$ is the prior probability assigned to the model. A common approach is to
assume the prior
probabilities for each model are equal or $p(M_t) = 1/T$ for all $t$ in which 
case
(\ref{eq:pmp}) is reduced to \eqref{eq:pmpeq}. In this case the posterior model 
probability for model $t$ is equal to the exponential of its negative LogS or
$p(M_t|x) = e^{-LogS(p(M_t|x))}$, so the performance of a forecast based on the
LogS is directly related to posterior model probability and may be used as an 
ensemble weight. For an observed event $x^*$, ensemble weights $(w_t)$ from 
\eqref{eq:bma} may be defined as $w_t := p(M_t|x^*)$.

\begin{equation}
\label{eq:pmp}
p(M_t|x) = \frac{p(x|M_t)p(M_t)}{p(x)}
         = \frac{p(x|M_t)p(M_t)}{\sum_{k=1}^T p(x|M_k)p(M_k)}
\end{equation}

@@

Using the illustrative example from Section \ref{section:tools}, 
the following code shows how
to use the posterior model probability to select weights and construct an 
ensemble distribution and score the ensemble forecast. Here again we take the 
observed value to be \texttt{3}.
The ensemble distribution
with components is show in figure \ref{fig:mixense}.

\begin{Schunk}
\begin{Sinput}
> #posterior model probability for calculating weights
> w1 <- pmdist1(ob)/(pmdist1(ob) + pmdist2(ob))
> w2 <- 1-w1
> w1
\end{Sinput}
\begin{Soutput}
[1] 0.5286434
\end{Soutput}
\begin{Sinput}
> w2
\end{Sinput}
\begin{Soutput}
[1] 0.4713566
\end{Soutput}
\begin{Sinput}
> #build ensemble with calculated weights
> ensdist <- distr::UnivarMixingDistribution(mdist1,
+                                            mdist2,
+                                            mixCoeff = c(w1,w2))
> #pdf and cdf for ensemble
> densdist <- function(x) {(distr::d(ensdist)(x))}
> pensdist <- function(x) {(distr::p(ensdist)(x))}
> #LogS for predictions at the realized observation
> -log(densdist(ob))
\end{Sinput}
\begin{Soutput}
[1] 1.678156
\end{Soutput}
\begin{Sinput}
> #CRPS for predictions at the realized observation
> CRPS(pensdist,y=ob)
\end{Sinput}
\begin{Soutput}
[1] 0.5486368
\end{Soutput}
\end{Schunk}

\begin{figure}[htbp]
\centerline{\includegraphics[scale=.15]{Images/mix_ense.png}}
\caption[Toy ensemble forecast]{Ensemble forecast made from forecast 1 and 
forecast 2 from Section \ref{section:tools}. The green line is the density 
component of mixture forecast 1 with weight 0.529. The 
red line is the density component of mixture forecast 2 with weight 
0.471. The blue line is the density of the ensemble.}
\label{fig:mixense}
\end{figure}

@@

\chapter{Retrospective analysis}
\label{section:retrostud}

For large collaborative forecast projects having already established the 
representation formats for forecasting, it may be difficult for individual
forecast teams to adjust to a mixture distribution format. There may be several
reasons for this, including that not all 
forecast modeling methods will produce forecasts which may conveniently be
represented by a mixture distribution.
In this section we attempt to assess whether or not any forecasts from the CDC
flu competition and the COVID-19 Forecast Hub were generated from one component
mixture distribution models. We do this by fitting one component mixture 
distributions to the forecasts and assessing how well the fit models represent
the forecasts.

Forecasters in both the CDC flu competition and the COVID-19 Forecast Hub do 
not include with their forecast submissions information about modeling methods 
or 
distributional assumptions. Thus the only information we have for fitting
distributions are bin
forecasts and quantile forecasts. We are unaware of formal statistical 
methods for fitting parametric distributions or mixture distributions to bin
distributions. Methods of fitting a distribution to quantiles 
include Bayesian Quantile Matching
\cite{nirwan2020bayesian}, step interpolation with exponential tails 
\cite{quinonero2005evaluating},
and the Method of Simulated Quantiles 
\cite{dominicy2013method}. These studies however lack claims that the methods
for fitting are statistically formal.
Because of this it should be noted that any conclusions made in 
this section may not be 
stated in terms of statistical certainty.

\section{CDC flu competition}
The CDC Retrospective Forecasts project at zoltrdata.com (cite??) contains over
869,638 probabilistic influenza-like illness forecasts for all combinations
of 11 regions 
in the United States and seven targets from 27 different modeling teams. These
include forecasts made during all flu seasons between October 2010 and December
2018. All forecasts are represented by bin distributions. 
We wanted to determine whether or not any of these forecasts were
generated from one component mixture distributions of continuous uniform, 
truncated normal (TN), truncated
lognormal (TL), or truncated gamma (TG) distribution families.
The process we followed for determining if a forecast was generated by one of
these common families was to first fit a distribution of that family to the bin
forecast and then measure close the fit was. The decsion to fit truncated 
distributions was due to all bin forecasts being assessed having a finite 
support.

To fit a distribution to a forecast we first minimize \eqref{eq:msd}. We call
\eqref{eq:msd} the mean square difference (MSD).
Here $F(\cdot| \hat{\theta})$ is a CDF, $p_i$ is the reported probability for 
the $i^{th}$ bin $B_i := [b_{i-1}, b_i)$ and $K$ is the number of bins.
The fitted parameter vector $\hat{\theta}$ is the solution to 
\eqref{eq:discfit}.
If a distribution was fit to the submitted binned 
prediction
and the MSD was less than a 
specified cutoff value, we
concluded that the bin forecast may have been discretized from the 
distribution.

\begin{equation}
  MSD = \sum_{i=1}^K (p_i - [F(b_i| \hat{\theta}) - F(b_{i-1}| \hat{\theta})])^2
  \label{eq:msd}
\end{equation}

\begin{equation}
\hat{\theta} = \arg\min_{\theta}\sum_{i=1}^K (p_i - 
[F(b_i; \theta) - F(b_{i-1}; \theta)])^2
\label{eq:discfit}
\end{equation}

To determine what values to use as cutoffs we conducted a study where 
bin distributions were discretized from known distributions, 
parameters were fit to the binned distrubtions and the MSD was calculated. This 
was done 1,000 times for the four distrubtion families considered and the cutoff 
value for each family was set as the value under which 95\% of MSD values fell.
The exact process is as follows.

For each of uniform, TN, TL, and 
TG distributions the following was
done 1,000 times. A set of 131 bins with interval widths of 
0.1 between 0 and 13 was constructed. 
A value $u$ was selected from a $\mbox{Unif(0,13)}$ distribution and $y$ from 
a $\mbox{Unif(.05,1.6)}$ distribution. 
$u$ and $y$ were taken as respectively 
the center and scale parameters of a TN distribution. 
For uniform, TL, and TG family
distributions, model parameters were solved for so that $u$ and $y$ 
were roughly the mean and standard deviation.
% Had we accounted for the changes
% in moment values from the truncation, the means and standard deviations could 
% have been exactly $\mu$ and $\sigma$. But we considered the differences small 
% enough that it didn't matter for our purpose.
With a known distribution with $\theta = (u,y)$, 
probabilities $p_i =F(b_i| \theta) - F(b_{i-1})$ 
where, were
calculated for each bin. A distribution from the same
family was fit to the bins by minimizing \eqref{eq:msd} with the resulting
distribution function $F(\cdot| \hat{\theta})$. 
The minimization was done using 
the \texttt{optim} function in the \texttt{R} \texttt{stats} package.
From the fit distribution
$\hat{p_i} = F(b_i; \hat{\theta}) - F(b_{i-1}; \hat{\theta})$ was computed for 
each of the 131 bins. Finally the MSD was calculated. 
Table \ref{table:bincutoffs}
below shows MSD value for which 95\% of all 1,000 MSDs fell below. Those values 
were selected as the 
cutoff values for declaring whether or not a bin distribution was discretized
from from a one component mixture distribution of that family.

\begin{table}[h!]
  \centering
  \begin{tabular}{l*{6}{c}r}
  Distribution          & MSD 95\%  \\
  \hline
  Uniform               & 8.809460e-05   \\
  Truncated Normal      & 1.126683e-07  \\
  Truncated Lognormal   & 3.877829e-06  \\
  Truncated Gamma       & 1.500152e-06  \\
  \end{tabular}
  \begin{center}
\begin{minipage}{10cm}
\captionsetup{font=scriptsize}
  \caption[Bin distribution cutoff values]{If a binned 
  one component mixture distribution is fit to a bin forecast
  and the MSD is smaller than
  the corresponding cutoff value listed here, we consider that bin 
  distribution to have been discretized from the fit mixture distribution.}
  \label{table:bincutoffs}
  \end{minipage}
  \end{center}
\end{table}

Of the 869,638 predictions from the CDC Retrospective Forecast project, we fit
each of uniform, TN, TL, and TG distributions to 11,715 of the individual 
predictions. From each of the 27 teams represented, we randomly selected 1,944
forecasts to fit. In many cases the \texttt{optim} function used to fit the 
distributions failed to converge, so of all forecasts we were only able to 
successfully fit distributions to 11,715 of them.
We calculated the MSD, and for each forecast the fit
distribution with the lowest of the four MSDs was considered the best fit. If 
the MSD from the best fit fell
below the corresponding cutoff value listed in \ref{table:bincutoffs} we 
concluded that 
the forecast was discretized from the fit distribution.

Table \ref{table:bincutoffs} shows the results of this analysis. 
Of the 11,715 binned distributions fit to the mixture distributions,
2,502 of those fits had MSD values below the values listed in Table
\ref{table:bincutoffs}. Thus we conclude that a proportion of 0.214 of those
forecasts were generated from a common parametric distribution. The results for 
the
11,715 fit distributions, which families the binned distributions were best
fit to and whether or not the fits produce an MSD below the cutoff value, 
are seen in table \ref{table:cdcresults}. Figure \ref{fig:binparamfits} is an
example of
the fit distributions to the same bin forecast.
